New insights into the Weddell Sea ecosystem applying a network approach

### 2022-12-13 Manuscript/Manuscript.Rmd
changes 13/12/2022
Updated

\introduction[Introduction]

@@

The statistical distribution that best fitted the empirical interaction strength distribution was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).

>>>>

# Introduction

<!-- about food webs and interaction strength -->
Building a network of feeding interactions among species is a fundamental step to understand ecological communities and is a valuable tool to manage ecosystems for conservation of biodiversity and functioning [@Thompson2012]. Although analyses considering presence/absence data on predator-prey interactions have provided insights about the structure and functioning of communities [e.g. @Kortsch2015; @Marina2018; @Cordone2020; @Rodriguez2022], more information is needed to effectively charaterise the ecosystems' dynamics and stability. In this regard, the intensity of the interactions between species or the interaction strength became of paramount importance in recent years [@Carrara2015; @Allesina2015].

<!-- General description of the Weddell Sea -->
The Weddell Sea is one of the most pristine and relatively unexplored hotspots of marine biodiversity in Antarctica and is still largely unprotected [@Teschke2021]. This region is less affected by sea surface warming compared with other areas like the Antarctic Peninsula, which is more exposed. If a climate change scenario is considered, the Weddell Sea continental shelf will be probably a sink area and a refuge for highly cold-adapted benthonic species [@Griffiths2017].

> * Food webs studies about Weddell Sea
> * Key species or species role

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).
